Graph Topological Aspects of Granger Causal Network Learning\\ \large Supplementary Material

### 2019-07-26 paper_theory/supplementary_material.tex
Essentially at the final version -- pending Ravi

\documentclass{statsoc}
\usepackage{fullpage}
\usepackage{ccfonts,eulervm}
\usepackage{tabularx}
\usepackage{xr}
\usepackage{chngcntr}
\usepackage{apptools}
\AtAppendix{\counterwithin{lemma}{section}}
\AtAppendix{\counterwithin{definition}{section}}
\AtAppendix{\counterwithin{equation}{section}}
\externaldocument{graph_topology_granger_causality}

@@

  \begin{enumerate}
  \item{$x_j \ngc x_i$}
  \item{$\forall \tau \in \N_+\ B_{ij}(\tau) = 0$ i.e. $\B_{ij}(z) = 0$}
  \item{$H_t^{i} \perp \H_{t - 1}^{j}\ |\ \H_{t - 1}^{-j}$}
  \item{$\linE{x_i(t)}{\H_{t - 1}^{-j}} = \linE{x_i(t)}{\H_{t - 1}}$}
  \end{enumerate}
\end{theorem}

@@

  $(a) \Rightarrow (b)$ follows as a result of the uniqueness of orthogonal
  projection (i.e. the best estimate is necessarily the coefficients
  of the model).  $(b) \Rightarrow (c)$ follows since in computing
  $(y - \linE{y}{\H_{t - 1}^{-j}})$ for $y \in H_t^i$ it is sufficient
  to consider $y = x_i(t)$ by linearity, then since
  $H_{t - 1}^i \subseteq \H_{t - 1}^{-j}$ we have
  $(x_i(t) - \linE{x_i(t)}{\H_{t - 1}^{-j}}) = v_i(t)$ since
  $\B_{ij}(z) = 0$.  The result follows since
  $v_i(t) \perp \H_{t - 1}$.  $(c) \iff (d)$ is a result of the equivalence
  in Definition \ref{lem:conditional_orthogonality_equivalence}.  And,
  $(d) \implies (a)$ follows directly from the Definition.
\end{proof}

@@

  From equation (\ref{eqn:ar_representation}), which we are assuming
  throughout the paper to be invertible, we can write

@@

  Let $S$ be a matrix with elements in $\{0, 1\}$ which represents the
  sparsity pattern of $\B(z)$, from lemma \ref{lem:adj_matrix} $S$ is
  the transpose of the adjacency matrix for $\gcg$ and hence
  $(S^k)_{ij}$ is non-zero if and only if $j \in \gpn{k}{i}$, and
  therefore $\B(z)^k_{ij} = 0$ if $j \not \in \gpn{k}{i}$.  Finally,
  since $\anc{i} = \bigcup_{k = 1}^n\gpn{k}{i}$ we see that
  $\A_{ij}(z)$ is zero if $j \not\in \anc{i}$.

@@

  then $\H_t^{(i)} \perp \H_t^{(j)}$, that is,
  $\forall s, \tau \in \Z_+\ \E[x_i(t - s)x_j(t - \tau)] = 0$.  Moreover,
  this means that $j \npwgc i$ and $\linE{x_j(t)}{\H_t^i} = 0$.
\end{proposition}

@@

\begin{lemma}
  \label{lem:vj_perp}
  Consider distinct nodes $i, j$ in a Granger-causality graph $\gcg$.
  If $j \not \in \anc{i}$, then $\H_t^{v_j} \perp \H_{t}^{i}$, and therefore
  for any causal filter $\Phi(z)$ we have

  \begin{align*}
    \linE{\Phi(z)v_j(t)}{\H_{t - 1}^i} &= 0\\
    \inner{x_i(t)}{\Phi(z)v_j(t)} & = 0.
  \end{align*}
\end{lemma}
\begin{proof}
  Fix $\tau, s \ge 0$, then by expanding with Equation \ref{eqn:ancestor_expansion}

@@

  \begin{equation*}
    \forall \psi \in \H_{t - 1}^j\ \inner{x_i(t) - \linE{x_i(t)}{\H_{t - 1}^i}}{\psi - \linE{\psi}{\H_{t - 1}^i}} = 0.
  \end{equation*}

  which by the orthogonality principle and by representing
  $\psi \in \H_{t - 1}^j$ via the action of some strictly causal filter
  $\Phi(z)$ on $x_j(t)$ is equivalent to

  \begin{equation}
    \label{eqn:proof_inner0}
    \inner{x_i(t)}{\Phi(z)x_j(t) - \linE{\Phi(z)x_j(t)}{\H_{t - 1}^i}} = 0.
  \end{equation}

@@

  \begin{equation*}
    \inner{x_i(t)}{\sum_{k \in \anc{j} \cup \{j\}} \Big(\Phi(z)\A_{jk}(z)v_k(t) - \linE{\Phi(z)\A_{jk}(z)v_k(t)}{\H_{t - 1}^i}\Big)}.
  \end{equation*}

@@

  We notice that for any $u$ having the properties $(a), (b)$ above,
  we must have $C_2(u) = \emptyset$ since if $k \in C_2(u)$ then
  $\exists w \in \anc{i} \cap \anc{k}$ (and
  $w \in \anc{i} \cap \anc{u}$, since $k \in \pa{u}$) such that
  $i \not \in \anc{k}$ and therefore there must be a path
  $\gcgpath{w}{k} \rightarrow u$ which does not contain $i$,
  contradicting property $(b)$.  Moreover, for any
  $u \in \big(\anc{j} \setminus \{i\}\big)$ and $k \in C_0(u)$,
  Proposition \ref{prop:ancestor_uncorrelated} shows that
  $H_t^i \perp \H_{t - 1}^j | \H_{t - 1}^i$.

  In order to establish $j \npwgc i$, choose an arbitrary element of
  $\H_{t - 1}^j$ and represent it via the action of a strictly causal
  filter $\Phi(z)$, i.e.  $\Phi(z) x_j(t) \in \H_{t - 1}^{(j)}$, by
  Theorem \ref{thm:granger_causality_equivalences} it suffices to show
  that

@@

  and this is $0$ since $\Phi(z)F(z)x_i(t) \in \H_{t - 1}^i$.

@@

  and therefore that $H_t^{(i)} \not\perp\ \H_{t - 1}^{(j)}\ |\ \H_{t - 1}^{(i)}$, which by theorem (\ref{thm:granger_causality_equivalences}) is enough to establish that $j \pwgc i$.

  Firstly, we will establish a representation of $x_i(t)$ that involves $x_j(t)$.  Denote by $a_{r + 1} \rightarrow a_r \rightarrow \cdots \rightarrow a_1 \rightarrow a_0$ with $a_{r + 1} \defeq j$ and $a_0 \defeq i$ the \textit{unique} $\gcgpath{j}{i}$ path in $\gcg$, we will expand the representation of equation (\ref{eqn:parent_expansion}) backwards along this path:

@@

  Using this representation to expand equation (\ref{eqn:cond_ortho_proof}), we obtain the following cumbersome expression:

@@

  Now since $F_{r + 1}(z) \ne 0$ by Theorem
  \ref{thm:granger_causality_equivalences}, and
  $F_{r + 1}(z)x_j(t) \not\in \H_{t - 1}^i$, we have by the
  Cauchy-Schwarz inequality that this expression is equal to $0$ if
  and only if

@@

  which can be expanded by equation \eqref{eqn:ancestor_expansion} to
  obtain (after cancelling all ancestors of $i$ other than $k$)

@@

% \begin{proposition}
%   \label{prop:persistence_converse}
%   Suppose $\gcg$ is a strongly causal DAG and that $x(t)$ is
%   persistent, then if there exists a $k$ which confounds $(i, j)$ we
%   have $i \pwgc j \implies j \pwgc i$.
% \end{proposition}
\begin{proof}
  Recalling Theorem \ref{thm:granger_causality_equivalences}, consider
  some $\psi \in \H_{t - 1}^j$ and represent it as
  $\psi(t) = F(z)x_j(t)$ for some strictly causal filter $F(z)$.
  Then

  \begin{align*}
    &\inner{\psi(t) - \linE{\psi(t)}{\H_{t - 1}^i}}{x_i(t) - \linE{x_i(t)}{\H_{t - 1}^i}}\\
    &\overset{(a)}{=} \inner{F(z)x_j(t)}{x_i(t) - \linE{x_i(t)}{\H_{t - 1}^i}}\\
    &\overset{(b)}{=} \inner{F(z)\big(\A_{jj}(z)v_j(t) + \sum_{k \in \anc{j}}\A_{jk}(z)v_k(t)\big)}{(1 - H_i(z))\big(\A_{ii}(z)v_i(t) + \sum_{\ell \in \anc{i}}\A_{i\ell}(z)v_\ell(t)\big)}\\
    &\overset{(c)}{=} \sum_{k \in \anc{i}\cap\anc{j}}\inner{F(z)\A_{jk}(z)v_k(t)}{(1 - H_i(z))\A_{ik}(z)v_k(t)},
  \end{align*}

  where $(a)$ applies the orthogonality principle, $(b)$ expands with
  Equation \eqref{eqn:ancestor_expansion} with
  $H_i(z)x_i(t) = \linE{x_i(t)}{H_{t - 1}^i}$, and $(c)$ follows by
  performing cancellations of $v_k(t) \perp v_\ell(t)$ and noting that
  by the contrapositive of Proposition \ref{prop:sc_graph_common_anc}
  we cannot have $i \in \anc{j}$ or $j \in \anc{i}$.

@@

  Through symmetric calculation, we can obtain the expression relevant
  to the determination of $i \pwgc j$ for $\phi \in \H_{t - 1}^i$ represented by the strictly causal filter $G(z): \phi(t) = G(z)x_i(t)$
  \begin{align*}
    &\inner{\phi(t) - \linE{\phi(t)}{\H_{t - 1}^j}}{x_j(t) - \linE{x_j(t)}{\H_{t - 1}^j}}\\
    &= \sum_{k \in \anc{i} \cap \anc{j}}\inner{G(z)\A_{ik}(z)v_k(t)}{(1 - H_j(z))\A_{jk}(z)v_k(t)},
  \end{align*}

  where $H_j(z)x_j(t) = \linE{x_j(t)}{\H_{t - 1}^j}.$

@@

\subsection{Efficient Model Estimation}
\label{sec:efficient_model_estimation}
In practice, the vast majority of computational effort involved in
implementing our estimation algorithm is spent calculating the error
estimates $\xi_i(p_i)$ and $\xi_{ij}(p_{ij})$.  This requires fitting a
total of $n^2p_{\text{max}}$ autoregressive models, where the most
naive algorithm (e.g. solving a least squares problem for each model)
for this task will consume $O(n^2p_{\text{max}}^4T)$ time, it is
possible to carry out this task in a much more modest
$O(n^2p_{\text{max}}^2 ) + O(n^2p_{\text{max}}T)$ time via the
autocorrelation method
\cite{hayes_statistical_digital_signal_processing} which substitutes
the following autocovariance estimates in the Yule-Walker
equations:\footnote{The particular indexing and normalization given in
  equation \ref{eqn:covariance_estimate} is critical to ensure
  $\widehat{R}$ is positive semidefinite.  The estimate can be viewed
  as calculating the covariance sequence of a signal multiplied by a
  rectangular window.}

@@

\subsection{Edge Probabilities and Error Rate Controls}
\label{sec:error_rate_control}
Denote $F_{ij}$ the Granger-causality statistic of equation
\ref{eqn:gc_statistics} with model orders chosen by the methods of
Section \ref{sec:model_order_selection}.  We assume that this
statistic is asymptotically $\chi^2(p_{ij})$ distributed (e.g. the
disturbances are Gaussian), and denote by $G$ the cumulative
distribution function thereof.  We will define the matrix

@@

    \Input{Estimates of pairwise Granger-causality statistics $F_{ij}$
      (eqn \ref{eqn:gc_statistics}).  Matrix of edge probabilities $P_{ij}$ (eqn \ref{eqn:edge_inclusion_probability}).  Hypothesis testing threshold $\delta$ chosen via the Benjamini-Hochberg criterion (Section \ref{sec:error_rate_control})}
    \Output{A strongly causal graph $\widehat{\gcg}$}
    \Initialize{$S = [n]$  \texttt{\# unprocessed nodes}\\
      $E = \emptyset$  \texttt{\# edges of }$\widehat{\gcg}$\\
      $k = 1$ \texttt{\# a counter used only for notation}}

@@

In reference to figure \ref{fig:simulation_results_comparison1} it
should not be overly surprising that our PWGC algorithm performs
better than the LASSO for the case of a strongly causal graph, since
in this case the theory from which our heuristic derives is valid.
However, the performance is still markedly superior in the case of a
more general DAG.  We would conjecture that a DAG having a similar
degree of sparsity as an SCG is ``likely'' to be ``close'' to an SCG,
in some appropriate sense.

@@

\clearpage
% \bibliography{\string~/Documents/academics/global_academics/global_bib}
\bibliography{paper_bib}
\end{document}

>>>>

\documentclass{statsoc}
\usepackage{fullpage}
\usepackage{ccfonts,eulervm}
\usepackage{tabularx}
\usepackage{xr}
\usepackage{chngcntr}
\usepackage{appendix}
\newcounter{lemma}
\newcounter{definition}
\counterwithin{lemma}{section}
\counterwithin{definition}{section}
\counterwithin{equation}{section}
\externaldocument{graph_topology_granger_causality}

@@

  \begin{enumerate}
  \item{$x_j \ngc x_i$}
  \item{$\forall \tau \in \N_+\ B_{ij}(\tau) = 0$ i.e. $\B_{ij}(z) = 0$}
  \item{$H_t^{(i)} \perp \H_{t - 1}^{(j)}\ |\ \H_{t - 1}^{(-j)}$}
  \item{$\linE{x_i(t)}{\H_{t - 1}^{(-j)}} = \linE{x_i(t)}{\H_{t - 1}}$}
  \end{enumerate}
\end{theorem}

@@

  $(a) \Rightarrow (b)$ follows as a result of the uniqueness of orthogonal
  projection (i.e. the best estimate is necessarily the coefficients
  of the model).  $(b) \Rightarrow (c)$ follows since in computing
  $(y - \linE{y}{\H_{t - 1}^{(-j)}})$ for $y \in H_t^{(i)}$ it is sufficient
  to consider $y = x_i(t)$ by linearity, then since
  $H_{t - 1}^{(i)} \subseteq \H_{t - 1}^{(-j)}$ we have
  $(x_i(t) - \linE{x_i(t)}{\H_{t - 1}^{(-j)}}) = v_i(t)$ since
  $\B_{ij}(z) = 0$.  The result follows since
  $v_i(t) \perp \H_{t - 1}$.  $(c) \iff (d)$ is a result of the equivalence
  in Definition \ref{lem:conditional_orthogonality_equivalence}.  And,
  $(d) \implies (a)$ follows directly from the Definition.
\end{proof}

@@

  From Equation \eqref{eqn:ar_representation}, which we are assuming
  throughout the paper to be invertible, we can write

@@

  Let $S$ be a matrix with elements in $\{0, 1\}$ which represents the
  sparsity pattern of $\B(z)$, from Lemma \ref{lem:adj_matrix} $S$ is
  the transpose of the adjacency matrix for $\gcg$ and hence
  $(S^k)_{ij}$ is non-zero if and only if $j \in \gpn{k}{i}$, and
  therefore $\B(z)^k_{ij} = 0$ if $j \not \in \gpn{k}{i}$.  Finally,
  since $\anc{i} = \bigcup_{k = 1}^n\gpn{k}{i}$ we see that
  $\A_{ij}(z)$ is zero if $j \not\in \anc{i}$.

@@

  then $\H_t^{(i)} \perp \H_t^{(j)}$, that is,
  $\forall s, \tau \in \Z_+\ \E[x_i(t - s)x_j(t - \tau)] = 0$.  Moreover,
  this means that $j \npwgc i$ and $\linE{x_j(t)}{\H_t^{(i)}} = 0$.
\end{proposition}

@@

\begin{lemma}
  \label{lem:vj_perp}
  Consider distinct nodes $i, j$ in a Granger-causality graph $\gcg$.
  If $j \not \in \anc{i}$, then $\H_t^{(v_j)} \perp \H_{t}^{(i)}$, and therefore
  for any causal filter $\Phi(z)$ we have

  \begin{align*}
    \linE{\Phi(z)v_j(t)}{\H_{t - 1}^{(i)}} &= 0\\
    \inner{x_i(t)}{\Phi(z)v_j(t)} & = 0.
  \end{align*}
\end{lemma}
\begin{proof}
  Fix $\tau, s \ge 0$, then by expanding with Equation \eqref{eqn:ancestor_expansion}

@@

  \begin{equation*}
    \forall \psi \in \H_{t - 1}^{(j)}\ \inner{x_i(t) - \linE{x_i(t)}{\H_{t - 1}^{(i)}}}{\psi - \linE{\psi}{\H_{t - 1}^{(i)}}} = 0.
  \end{equation*}

  which by the orthogonality principle and by representing
  $\psi \in \H_{t - 1}^{(j)}$ via the action of some strictly causal filter
  $\Phi(z)$ on $x_j(t)$ is equivalent to

  \begin{equation}
    \label{eqn:proof_inner0}
    \inner{x_i(t)}{\Phi(z)x_j(t) - \linE{\Phi(z)x_j(t)}{\H_{t - 1}^{(i)}}} = 0.
  \end{equation}

@@

  \begin{equation*}
    \inner{x_i(t)}{\sum_{k \in \anc{j} \cup \{j\}} \Big(\Phi(z)\A_{jk}(z)v_k(t) - \linE{\Phi(z)\A_{jk}(z)v_k(t)}{\H_{t - 1}^{(i)}}\Big)}.
  \end{equation*}

@@

  We notice that for any $u$ having the properties $(a), (b)$ above,
  we must have $C_2(u) = \emptyset$ since if $k \in C_2(u)$ then
  $\exists w \in \anc{i} \cap \anc{k}$ (and
  $w \in \anc{i} \cap \anc{u}$, since $k \in \pa{u}$) such that
  $i \not \in \anc{k}$ and therefore there must be a path
  $\gcgpath{w}{k} \rightarrow u$ which does not contain $i$,
  contradicting property $(b)$.  Moreover, for any
  $u \in \big(\anc{j} \setminus \{i\}\big)$ and $k \in C_0(u)$,
  Proposition \ref{prop:ancestor_uncorrelated} shows that
  $H_t^{(i)} \perp \H_{t - 1}^{(j)} | \H_{t - 1}^{(i)}$.

  In order to establish $j \npwgc i$, choose an arbitrary element of
  $\H_{t - 1}^{(j)}$ and represent it via the action of a strictly causal
  filter $\Phi(z)$, i.e.  $\Phi(z) x_j(t) \in \H_{t - 1}^{(j)}$, by
  Theorem \ref{thm:granger_causality_equivalences} it suffices to show
  that

@@

  and this is $0$ since $\Phi(z)F(z)x_i(t) \in \H_{t - 1}^{(i)}$.

@@

  and therefore that $H_t^{(i)} \not\perp\ \H_{t - 1}^{(j)}\ |\ \H_{t - 1}^{(i)}$, which by Theorem (\ref{thm:granger_causality_equivalences}) is enough to establish that $j \pwgc i$.

  Firstly, we will establish a representation of $x_i(t)$ that involves $x_j(t)$.  Denote by $a_{r + 1} \rightarrow a_r \rightarrow \cdots \rightarrow a_1 \rightarrow a_0$ with $a_{r + 1} \defeq j$ and $a_0 \defeq i$ the \textit{unique} $\gcgpath{j}{i}$ path in $\gcg$, we will expand the representation of Equation \eqref{eqn:parent_expansion} backwards along this path:

@@

  Using this representation to expand Equation \eqref{eqn:cond_ortho_proof}, we obtain the following cumbersome expression:

@@

  Now since $F_{r + 1}(z) \ne 0$ by Theorem
  \ref{thm:granger_causality_equivalences}, and
  $F_{r + 1}(z)x_j(t) \not\in \H_{t - 1}^{(i)}$, we have by the
  Cauchy-Schwarz inequality that this expression is equal to $0$ if
  and only if

@@

  which can be expanded by Equation \eqref{eqn:ancestor_expansion} to
  obtain (after cancelling all ancestors of $i$ other than $k$)

@@

% \begin{proposition}
%   \label{prop:persistence_converse}
%   Suppose $\gcg$ is a strongly causal DAG and that $x(t)$ is
%   persistent, then if there exists a $k$ which confounds $(i, j)$ we
%   have $i \pwgc j \implies j \pwgc i$.
% \end{proposition}
\begin{proof}
  Recalling Theorem \ref{thm:granger_causality_equivalences}, consider
  some $\psi \in \H_{t - 1}^{(j)}$ and represent it as
  $\psi(t) = F(z)x_j(t)$ for some strictly causal filter $F(z)$.
  Then

  \begin{align*}
    &\inner{\psi(t) - \linE{\psi(t)}{\H_{t - 1}^{(i)}}}{x_i(t) - \linE{x_i(t)}{\H_{t - 1}^{(i)}}}\\
    &\overset{(a)}{=} \inner{F(z)x_j(t)}{x_i(t) - \linE{x_i(t)}{\H_{t - 1}^{(i)}}}\\
    &\overset{(b)}{=} \inner{F(z)\big(\A_{jj}(z)v_j(t) + \sum_{k \in \anc{j}}\A_{jk}(z)v_k(t)\big)}{(1 - H_i(z))\big(\A_{ii}(z)v_i(t) + \sum_{\ell \in \anc{i}}\A_{i\ell}(z)v_\ell(t)\big)}\\
    &\overset{(c)}{=} \sum_{k \in \anc{i}\cap\anc{j}}\inner{F(z)\A_{jk}(z)v_k(t)}{(1 - H_i(z))\A_{ik}(z)v_k(t)},
  \end{align*}

  where $(a)$ applies the orthogonality principle, $(b)$ expands with
  Equation \eqref{eqn:ancestor_expansion} with
  $H_i(z)x_i(t) = \linE{x_i(t)}{H_{t - 1}^{(i)}}$, and $(c)$ follows by
  performing cancellations of $v_k(t) \perp v_\ell(t)$ and noting that
  by the contrapositive of Proposition \ref{prop:sc_graph_common_anc}
  we cannot have $i \in \anc{j}$ or $j \in \anc{i}$.

@@

  Through symmetric calculation, we can obtain the expression relevant
  to the determination of $i \pwgc j$ for $\phi \in \H_{t - 1}^{(i)}$ represented by the strictly causal filter $G(z): \phi(t) = G(z)x_i(t)$
  \begin{align*}
    &\inner{\phi(t) - \linE{\phi(t)}{\H_{t - 1}^{(j)}}}{x_j(t) - \linE{x_j(t)}{\H_{t - 1}^{(j)}}}\\
    &= \sum_{k \in \anc{i} \cap \anc{j}}\inner{G(z)\A_{ik}(z)v_k(t)}{(1 - H_j(z))\A_{jk}(z)v_k(t)},
  \end{align*}

  where $H_j(z)x_j(t) = \linE{x_j(t)}{\H_{t - 1}^{(j)}}.$

@@

\subsection{Efficient Model Estimation}
\label{sec:efficient_model_estimation}
In practice, the vast majority of computational effort involved in
implementing our estimation algorithm is spent calculating the error
estimates $\xi_i(p_i)$ and $\xi_{ij}(p_{ij})$.  This requires fitting a
total of $n^2p_{\text{max}}$ autoregressive models, where the most
naive algorithm (e.g. solving a least squares problem for each model)
for this task will consume $O(n^2p_{\text{max}}^4T)$ time, it is
possible to carry out this task in a much more modest
$O(n^2p_{\text{max}}^2 ) + O(n^2p_{\text{max}}T)$ time via the
autocorrelation method
\cite{hayes_statistical_digital_signal_processing} which substitutes
the following autocovariance estimates in the Yule-Walker
equations:\footnote{The particular indexing and normalization given in
  Equation \eqref{eqn:covariance_estimate} is critical to ensure
  $\widehat{R}$ is positive semidefinite.  The estimate can be viewed
  as calculating the covariance sequence of a signal multiplied by a
  rectangular window.}

@@

\subsection{Edge Probabilities and Error Rate Controls}
\label{sec:error_rate_control}
Denote $F_{ij}$ the Granger-causality statistic of Equation
\eqref{eqn:gc_statistics} with model orders chosen by the methods of
Section \ref{sec:model_order_selection}.  We assume that this
statistic is asymptotically $\chi^2(p_{ij})$ distributed (e.g. the
disturbances are Gaussian), and denote by $G$ the cumulative
distribution function thereof.  We will define the matrix

@@

    \Input{Estimates of pairwise Granger-causality statistics $F_{ij}$
      (eqn. \ref{eqn:gc_statistics}).  Matrix of edge probabilities $P_{ij}$ (eqn. \ref{eqn:edge_inclusion_probability}).  Hypothesis testing threshold $\delta$ chosen via the Benjamini-Hochberg criterion (Section \ref{sec:error_rate_control})}
    \Output{A strongly causal graph $\widehat{\gcg}$}
    \Initialize{$S = [n]$  \texttt{\# unprocessed nodes}\\
      $E = \emptyset$  \texttt{\# edges of }$\widehat{\gcg}$\\
      $k = 1$ \texttt{\# a counter used only for notation}}

@@

In reference to Figure \ref{fig:simulation_results_comparison1} it
should not be overly surprising that our PWGC algorithm performs
better than the LASSO for the case of a strongly causal graph, since
in this case the theory from which our heuristic derives is valid.
However, the performance is still markedly superior in the case of a
more general DAG.  We would conjecture that a DAG having a similar
degree of sparsity as an SCG is ``likely'' to be ``close'' to an SCG,
in some appropriate sense.

@@

\clearpage
\bibliography{paper_bib}
\end{document}
